FinalManuscript_DISCS_UG

### 2018-06-24 parts/01_introduction_03objectives.tex
Completed scope and limitations

A paper published in 2009 by Ziad, et. al. presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV) which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem \cite{ziad_cryptoimg:_2016}. While \textit{CryptoImg} demonstrates that various image manipulation operations are possible in a homomorphic system, we believe this study can be extended by considering other known homomorphic encryption schemes, such as an elliptic curve and ElGamal based cryptosystem presented by Li, et. al. \cite{li_elliptic_2012}, and the fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}. Our study aims to provide an objective comparision of various homomorphic cryptosystems currently in the literature, as they would be used in encrypted image manipulation.
Furthermore, one of the main problems in homomorphic encryption is the practicality of homomorphic encryption schemes. Homomorphic cryptosystems are known to be slower compared to other cryptosystems \cite{sen_homomorphic_2013}.
Taking the above into account, in this study, we wish to
\begin{enumerate}
    \item Compare the applicability of known homomorphic encryption schemes to common image processsing operations, in other words, determine which schemes permit more image processing operations;
		\item Compare the security of common image processsing operations under known homomorphic encryption schemes, using established statistical methods in image encryption;
    \item Compare the efficiency of common image processsing operations under known homomorphic encryption schemes;
    \item Create a plug-in for OpenCV to allow for convenient use of these homomorphic encryption schemes.
\end{enumerate}

>>>>

A paper published in 2009 by Ziad, et. al. presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV) \cite{opencv_library} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem \cite{ziad_cryptoimg:_2016}. While \textit{CryptoImg} demonstrates that various image manipulation operations are possible in a homomorphic system, we believe this study can be extended by considering other known homomorphic encryption schemes, such as an elliptic curve and ElGamal based cryptosystem presented by Li, et. al. \cite{li_elliptic_2012}, and the fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}. Our study aims to provide an objective comparision of various homomorphic cryptosystems currently in the literature, as they would be used in encrypted image manipulation.
Furthermore, one of the main problems in homomorphic encryption is the practicality of homomorphic encryption schemes. Homomorphic cryptosystems are known to be slower compared to other cryptosystems \cite{sen_homomorphic_2013}.
Taking the above into account, in this study, we wish to
\begin{enumerate}
    \item Compare the applicability of known homomorphic encryption schemes to common image processsing operations, in other words, determine which schemes permit more image processing operations;
		\item Compare the security of common image processsing operations under known homomorphic encryption schemes, using established statistical methods in image encryption;
    \item Compare the efficiency of common image processsing operations under known homomorphic encryption schemes;
    \item Create a plug-in for OpenCV to allow for convenient use of these homomorphic encryption schemes.
\end{enumerate}

### 2018-06-24 parts/01_introduction_04significanceofstudy.tex
Completed scope and limitations

If the Research Objective answers the ‘what’ of your study, this section aims to answer the ‘why’. Generally, you may address this significance in terms of its significance in the area of Computer Science and the community. However, other questions which you may also use to guide your significance are the following: “Why is your study important?” “What will your study contribute to the field of Computer Science?” “How will your study benefit not only your intended audience, but the general public, especially our country?”

>>>>

The results of the study will provide

### 2018-06-24 parts/01_introduction_05scopeandlimitations.tex
Completed scope and limitations

\section{Scope and Limitations of the Study}

Our study will be limited in terms of the cryptosystems to be tested, the image processing operations we will implement, and the statistical tests we will use to

\textbf{insert listing here}

Our library for OpenCV will be implmented in the C++ programming language.

\textbf{insert other limitations here}

>>>>

\section{Scope and Limitations of the Study}
Our study will be limited in terms of the cryptosystems to be tested, the image processing operations we will implement, and the statistical tests we will use to gauge the security of the cryptosystems. Below is a listing of the scope of the study.

\subsection{Scope of Testing}
We will implement and test the following algorithms:
\begin{enumerate}
	\item A modified version of the Paillier cryptosystem \cite{} which supports floating-point operations, used in \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}.
	\item An elliptic curve and ElGamal based cryptosystem for homomorphic encryption presented by Li, et. al. \cite{li_elliptic_2012}.
	\item A fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}, which is an improvement on the original lattice-based cryptosystem presented by Gentry \cite{gentry_fully_2009}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Image adjustment
	\item Operations based on convolution
	\item Morphological operations
\end{enumerate}
We will adopt the benchmark for evaluating the performance and security of image encryption schemes presented by Ahmed, et. al \cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature \cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	\item Tests for preservation of image quality after encryption and decryption.
	\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
		\item Noise tolerance
	\end{enumerate}
	\item Tests for cryptographic security
	\begin{enumerate}
		\item Information entropy analysis
		\item Correlation coefficient analysis
		\item Differential analysis (number of pixel change rate (NPCR), universeral average change intensity (UACI))
	\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the review of related literature.

Images used for testing will be obtained from a database maintained by Gonzalez, et. al. \cite{gonzalez_image_nodate}. Both greyscale and color images will be used.

\subsection{Scope of Implementation}
Our library for OpenCV will be implemented in the C++ programming language.
